Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-16 cloneoverflow-latex/cloneoverflow.tex
Updated latex with chart

We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine them into a single file. GCF provides a common format for clones which enable us to reuse scripts that analyse clone reports from Simian and NiCad. Moreover, using GCF, other additional clone detectors can be adopted, if needed, without any changes in the analysis. Simian do not provide an option to detect inter clones between two locations. Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas project. In this step, all intra clone pairs within Stack Overflow and open source projects are removed. NiCad provides an option to detect inter clones so no pruning is needed. Next, clone pairs reported from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}. This step generates \textbf{agreement-based clone pairs}. They are clones with highest confidence since they receive agreement from both tools. Then, clone pairs reported by Simian and NiCad that do not find agreement are filtered by size of minimum 10 lines. This step generates \textbf{non agreement-based clone pairs}. The non agreement-based clone pairs are clones with less confidence than agreement-based ones. Finally, agreement-based and non agreement-based clone pairs are looked at and classified manually by the first author.

@@

\subsubsection{Agreement-based Clone Filtering}
The number of detected clones between two datasets  can be very large. In our study, there are totally 266,837,480 clone pairs reported. It is infeasible for human to manually validate all of them. One can do sampling of clones from this huge clone pair set. However, they may end up having most of them false positive clones. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find agreement of two clone pairs, we resort to an approach proposed in a study by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions introduced in the original paper.

@@

\section{Results}

@@

\begin{table}
	\centering
	\caption{13 Qualitas projects that have been cloned as examples on Stack Overflow with their respective licenses}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|p{4cm}}
		\hline 
		Project & Version & Licenses (no.~of files) \\
		\hline
%		apache-ant & 1.8.4 & Apache2.0 \\
%		apache-log4j & 1.2.16 & \\
		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
		\hline
		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
		\hline
		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
		\hline
		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
		\hline
		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
		\hline
		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
		\hline
%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
		\hline
		jung2 & 2-0-1 & N/A \\
		\hline
		junit & 4.11 & None (160), Unknown (4)  \\
		\hline
		poi & 3.6 & Apache-2 (2,002), None (5) \\
		\hline
		spring & 3.0.5 & Apache-2 (2,982) \\
		\hline
		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
		\hline
		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
%		weka & 3-7-9 & \\
		\hline
	\end{tabular} %
	%	}
\end{table}

%\begin{table*}
%	\centering
%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
%	\label{t:new_and_old}
%	%	\resizebox{\columnwidth}{!}{%
%	\small
%	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
%		\hline 
%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
%			\hline
%			apache-jmeter & 2. 9 & & & & & \\
%			apache-log4j & 1.2.16 & & & & & \\
%			apache-maven & 3.0 & & & & & \\
%			apache-roller & 4.0.1 & & & & & \\
%			apache-tomcat & 7.0.2 & & & & & \\
%			jhotdraw & 7.5.1 & & & & & \\
%			jrefactory & 2.9.19 & & & & & \\
%			jruby & 1.5.2 & & & & & \\
%			jspwiki & 2.8.4 & & & & & \\
%			jstock & 1.0.7c & & & & & \\
%			jsxe & 04\_beta & & & & & \\
%			jtopen & 7\_1 & & & & & \\
%			jung2 & 2\_0\_1 & & & & & \\
%			lucene & 4.3.0 & & & & & \\
%			marauroa & 3.8.1 & & & & & \\
%			megamek & 0.35.18 & & & & & \\
%			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
%			myfaces-core & 2.0.2 & & & & & \\
%			nakedobjects & 4.0.0 & & & & & \\
%			nekohtml & 1.9.14 & & & & & \\
%			netbeans & 6.9.1 & & & & & \\
%			openjms & 0.7.7-beta-1 & & & & & \\
%			oscache & 2.4.1 & & & & & \\
%			picocontainer & 2.10.2 & & & & & \\
%			pmd & 4.2.5 & & & & & \\
%			poi & 3.6 & & & & & \\
%			pooka & 080505 & & & & & \\
%			proguard & 4.5.1 & & & & & \\
%			quartz & 1.8.3 & & & & & \\
%			quickserver & 1.4.7 & & & & & \\
%			quilt & 0.6-a-5 & & & & & \\
%			rssowl & 2.0.5 & & & & & \\
%			sablecc & 3.2 & & & & & \\
%			sandmark & & & & & & \\
%			spring-framework & 3.0.5 & & & & & \\
%			struts2 & 2.2.1-all & & & & & \\
%			sunflow & 0.07.2 & & & & & \\
%			tapestry & 5.1.0.5 & & & & & \\
%			trove & 2.1.0 & & & & & \\
%			velocity & 1.6.4 & & & & & \\
%			wct-package & 1.5.2 & & & & & \\
%			webmail & 0.7.10 & & & & & \\
%			weka & 3-7-9 & & & & & \\
%			xalan-j & 2\_7\_1 & & & & & \\
%			xerces-J & 2.10.0 & & & & & \\
%			xmojo & 5.0.0 & & & & & \\
%			\hline 
%		\end{tabular} %
%%	}
%\end{table*}

%\subsection{Agreement based clone pairs vs. Non agreement based clone pairs}

%The agreement-based clone pairs are the ones discovered using Bellon's good-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}. Non-agreement based clone pairs are the ones that are solely reported by a single tool. The agreement-based pairs provide higher confident that they are real clones than the non-agreement based ones.

\subsection{Agreement-based clone pairs}

Agreement-based clone pairs are clone pairs that pass Bellon's criteria and selected for manual investigation. We select a threshold \textit{p} of 0.7 for both good and ok-match similar to the original study \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. NiCad generated errors and stopped processing while it was analysing some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ unsuccessfully detected clones in 6 projects due to clustering errors. For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects. As a result, we did not have NiCad clone candidates for 6 (\textit{df}) and 27 projects (\textit{EvCl}) in the agreement-based clone pairs. Unfortunately, this also has an effect to Simian clone candidates of the same projects to be removed from the agreement-based clone pairs since they do not have matching clone pairs. The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are depicted in \Cref{fig:venn4_orig_good}. There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. ok-match clone pairs subsume the good-match pairs according to the criteria. As a result, there are 23,868 clone pairs, which are 3,800 pairs from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. Between the four configuration sets, there are a few clone pairs that are shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreement-based clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian & NiCad & good-match & ok-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{df} & \textit{df} & 10 	& 9062 \\ 
		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
		\hline
	\end{tabular}
\end{table}

@@

\subsubsection{Classifications of online code clones}

\begin{table*}
	\centering
	\caption{Classifications of online code clones}
	\label{tab:classification_scheme}
	\begin{tabular}{|c|p{13cm}|}
		\hline 
		Category & Descriptions \\ 
		\hline 
		A & Code in Stack Overflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
		\hline 
		A' & Code in Qualitas is copied from Stack Overflow (S $\rightarrow$ Q). \\ 
		\hline 
		B & Clone pair is exactly identical or highly similar and may be copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
		\\ 
		\hline 
		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
		\\ 
		\hline 
		D & Code is a boiler-plate or IDE auto-generated.
		\\ 
		\hline 
		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
		\\ 
		\hline 
		F & Accidental similarity, false clone \\ 
		\hline 
	\end{tabular} 
\end{table*}

We need an appropriate classification scheme to be able to meaningfully manually categorise the selected clone candidates. We adapted the classifications from a study by Kapser et al. \cite{Kapser2006}. The online code clone classification scheme is described in \Cref{tab:classification_scheme}. Due to differences in the experimental settings of the study, we adopted some of the original classifications and added a few more classifications to match with our datasets and context. The final seven categories (A--F) have been observed to be common clone patterns found from a manual check of 100 random sample clone pairs. Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'. Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying. Category C is a clone pair that has information confirming of copying but from the same external source. Category D is a clone pair that is either boiler-plate code (e.g. \verb|equals()| methods, or getters and setters) or IDE-generated (e.g. GUI initialisation). Category E are clones created by inheriting the same super class or implementing the same interface. They usually share similar overriding methods. The last category, category F, are false clones that have accidental similarity after code normalisation or other causes. Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.

\subsubsection{Manual investigation of agreement-based clone pairs}

The first author who has been working on clone detection research for two years takes the role of an investigator who performs manual investigation. Following the classification scheme, the investigator manually goes through each agreement-based clone pair, looks at the clones, and chooses the most appropriate category for the pair. A relevant and useful observation is also recorded for each clone pair. The classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated 2,261 good-match clone pairs. There is one clone pair found to be copied from a Qualitas project to Stack Overflow, 4 pairs that are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code), and 3 pairs that are copied from external sources. The rest are false positive clones. 58 clone pairs are found to \verb|equals()| methods, or getters and setters. Six pairs are similar code from inheritance of the same superclass or implementing the same interface. Finally, 2,189 clone pairs are false clones.

For the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.  According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference. We thus decided to leave this configuration out of the ok-match manual investigation. There are totally 4,625 ok-match pairs that were investigated. The 49 true positive pairs found are combinations of 8, 33, and 8 clone pairs in category A, B, and C respectively.

We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying. We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts. We found that all Stack Overflow posts were created after their respectively Qualitas Java files \FIXME{check again since the dataset is updated}. This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from an external source to both Stack Overflow and Qualitas independently. There is no clone pairs found in A' category.

@@

@@

\section{Effects of online code clone}

In this study, we are interested in the effects of online code clones to software development. From the manual investigation of 184 true online clone pairs, we found that there are two potential issues: stale online code, and software licensing violation.

>>>>

We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine them into a single file. GCF provides a common format for clones which enable us to reuse scripts that analyse clone reports from Simian and NiCad. Moreover, using GCF, other additional clone detectors can be adopted, if needed, without any changes in the analysis. Simian do not provide an option to detect inter clones between two locations. Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas project. In this step, all intra clone pairs within Stack Overflow and open source projects are removed. NiCad provides an option to detect inter clones so no pruning is needed. Next, clone pairs reported from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}. This step generates \textbf{agreed clone pairs}. They are clones with highest confidence since they receive agreement from both tools. Then, clone pairs reported by Simian and NiCad that do not find agreement are filtered by size of minimum 10 lines. This step generates \textbf{disagreed clone pairs}. The disagreed clone pairs are clones with less confidence than agreed ones. Finally, agreed and disagreed clone pairs are looked at and classified manually by the first author.

@@

\subsubsection{Clone Candidate Filtering Using Agreement}
Usually a number of clones detected between two large-scale datasets  can be huge. In our study, there are totally 266,837,480 clone pairs reported. It is infeasible for human to manually validate all of them. One can do sampling of clones from this huge clone pair set. However, they may end up having most of them false positive clones. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreed clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find an agreement of two clone pairs, we resort to the approach of clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions of good- and ok-match introduced in the original paper.

@@

\section{Results and discussion}

We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors. To answer RQ1 and RQ2 together, we compute statistics of clone discovered by the tools and the true clone pairs confirmed by manual investigation. In the manual investigation process, we proposed an online clone classification scheme derived from common patterns found in online code clones. For RQ3, we look at the true positive clone pairs carefully and compare them to their latest versions. This is to see if the cloned code is still up-to-date. We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
\subsection{RQ1: Online code clones}

@@

\subsubsection{Agreed clone pairs}

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.  Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match\cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. We found that NiCad generates errors and stopped processing while it is analysing some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ could not detect clones in 6 projects due to clustering errors. For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects. As a result, we did not have NiCad clone candidates in the agreed clone pairs for 6 and 27 projects with \textit{df} and \textit{EvCl} configurations respectively. This affected Simian clone candidates of the same projects to be removed from the agreed clone pairs as well since they could not have matching clone pairs.

The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. According to the definition, ok-match clone pairs always subsume the good-match pairs. As a result, there are 29,944 ok-match clone pairs. 9,062 pairs are from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs are from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 are pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs are from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.

@@

\begin{table}[H]
	\centering
	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
	\label{t_agreed_good_clone_pairs}
	\small
	\begin{tabular}{l|l|r|r}
		\hline
		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
		\hline
		Simian & NiCad & good-match & ok-match \\
		%\hline
		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		\textit{df} & \textit{df} & 10 	& 9062 \\ 
		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
		\hline
		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
		\hline
		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
		\hline
	\end{tabular}
\end{table}

@@

\subsubsection{Disagreed clone pairs}
%In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations. However, only 10 of them appear in the new results using tool's agreement. Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.

The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool. The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported. They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs. With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively). They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.

Even choosing only the default configurations, the number of clone pair candidates are still very large. We hence apply two pruning filters: clone size, and similarity threshold. For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}. The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines). The second filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration. %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%. %Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.

% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
For Simian$_{df}$, there are 20,348 clone pairs after using 10--line filter. Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded. We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expressions. We managed to reduce the number to 871 clone pairs remaining for manual investigation. 
% 7062 + 22187 + 6755 =  36004 %
For NiCad$_{df}$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. We thus filter NiCad's clones by using similarity threshold. We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs. %However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well. So . Using 80\% similarity, there are totally 166 pairs left. 
There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation. The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.

\begin{table}
	\centering
	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
	\label{tab:classification_indv_stats}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2.4cm}|r|r|r}
		\hline 
		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
		%\hline 
		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
		\hline
		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
		\hline
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
		\hline
	\end{tabular} %
	}
\end{table}

\subsection{RQ2: Classifications of online code clones}

\begin{table}
	\centering
	\caption{Seven categories of online code clones}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{|c|p{8cm}|}
			\hline 
			Cat. & Descriptions \\ 
			\hline 
			A & Cloned from Qualitas to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			A' &Cloned from Stack Overflow to Qualitas (S $\rightarrow$ Q). \\ 
			\hline 
			B & Cloned from each other or from an external source \textit{X} (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			C & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			D & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			E & Inheritance, interface implementation 
			\\ 
			\hline 
			F & Accidental similarity, false clones by normalisation \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand. We started by studying the 8 patterns of cloning from Kapser et al. \cite{Kapser2006}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using Simian$_{df}$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size. We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed. We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new categories observed as common cloning patterns from the manual investigation. The seven categories ranging from A--F presented in \Cref{tab:classification_scheme}. Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'. Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying. Category C is a clone pair that has information confirming of copying from the same external source. Category D is a clone pair that is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation). Category E are clones created by inheriting the same super class or implementing the same interface. They usually share similar overriding methods. The last category, category F, is a false clone pair. They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process. Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.

\subsubsection{Manual investigation of clone pair candidates}

The first author who has been working on clone detection research for two years takes the role of an investigator performing manual investigation. Following the classification scheme, the investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate category for the pair. A relevant and useful observation is also recorded for each clone pair.

\textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated 2,261 good-match clone pairs. There is one clone pair in category A which is found to be copied from a Qualitas project to Stack Overflow. Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as category B. We found 3 pairs in category C that are copied from external sources. The rest are false positive clones. 58 clone pairs are found to be \verb|equals()| methods, or getters and setters, category D. Six pairs are similar code from inheritance of the same superclass or implementing the same interface, category E. Finally, 2,189 clone pairs are categorised to E which means they are false clones.

For the ok-match clone pairs, we could not feasibly investigate all 23,868 pairs manually.  According to the manual investigation of good-match pairs, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference. We thus decided to leave this configuration out of the ok-match manual investigation. There are totally 4,625 ok-match pairs that were investigated. The 47 true positive pairs found are combinations of 8, 29, and 10 clone pairs in category A, B, and C respectively.

\FIXME{Maybe remove?} We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying. We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts. We found that all Stack Overflow posts were created after their respectively Qualitas Java files \FIXME{check again since the dataset is updated}. This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from an external source to both Stack Overflow and Qualitas independently. There is no clone pairs found in A' category.

@@

\begin{table}
	\centering
	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|p{4cm}}
		\hline 
		Project & Version & Licenses (no.~of files) \\
		\hline
		%		apache-ant & 1.8.4 & Apache2.0 \\
		%		apache-log4j & 1.2.16 & \\
		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
		\hline
		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
		\hline
		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
		\hline
		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
		\hline
		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
		\hline
		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
		\hline
		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
		\hline
		%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
		\hline
		jung2 & 2-0-1 & N/A \\
		\hline
		junit & 4.11 & None (160), Unknown (4)  \\
		\hline
		poi & 3.6 & Apache-2 (2,002), None (5) \\
		\hline
		spring & 3.0.5 & Apache-2 (2,982) \\
		\hline
		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
		\hline
		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
		%		weka & 3-7-9 & \\
		\hline
	\end{tabular} %
	%	}
\end{table}

@@

\subsection{RQ3: Effects of online code clones}

In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow. From the manual investigation, we found 523 true positive online clone pairs. With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.

\subsubsection{Outdated code clones}
Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated. This is a normal issue driving the development of clone detection. We need to locate clones to be able to update them according to their updated original code \cite{somewhere,somewhere_else}. However, in this situation, the clones are more pervasive on Stack Overflow posts and more difficult to detect due to its large scale and the mix of natural language and source code. Since code can be updated due to various possible reasons including bug fixing, this poses a problem if developers reuse a cloned code snippet from Stack Overflow without knowing that it is outdated. %They might also introduce the same unfixed bug(s) into the software. 
They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce the same later-be-fixed bug(s) into their software.
